Telemetry Module for Solar Vehicle

### 2021-06-17 documentation/FinalPaper/paper.tex
Updates from Overleaf

\section{Components}
\subsection{CAN bus}
The CAN network in the SCU enables the all the car's processing nodes to send and receive data without a host computer. This is possible thanks to the special structure of the CAN message.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{documentation/images/EnhancedShockburst.pdf}
    \caption{The Enhanced Shockburst$^\copyright$ packet structure.}
    \label{fig:shockburst}
\end{figure}

@@

\subsection{Microcontrollers} % Steffan
Finally, Teensy 3.6 and 4.0 microcontrollers are used as connection hubs in the SCU and SVU respectively. The boards can interact with the various components through an SPI interface to gather, process and transmit large amounts of data. Being based on the Arduino framework, both Teensys offer support for numerous protocols and software libraries to ease the implementation of our design.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/prime_tabel.pdf}
    \caption{Valid combinations of prime numbers, marked by OOOOOO}
    \label{fig:prime_tabel}
\end{figure}

>>>>

\section{Components}

\subsection{Microcontrollers} % Steffan
We use Teensy 3.6 and 4.0 microcontrollers as connection hubs in the SCU and SVU respectively. The boards can interact with the various components through an SPI interface to gather, process and transmit large amounts of data. Being based on the Arduino framework, both Teensys offer support for numerous protocols and software libraries to ease the implementation of our design.

\subsection{CAN bus}
The CAN network in the SCU enables the all the car's processing nodes to send and receive data without a host computer. This is possible thanks to the special structure of the CAN message.

@@

\begin{figure}[h]
    \centering
    \includegraphics[trim={0 2cm 0 0 },clip]{documentation/images/EnhancedShockburst.pdf}
    \caption{The Enhanced Shockburst$^\copyright$ packet structure.}
    \label{fig:shockburst}
\end{figure}

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/prime_tabel.png}
    \caption{Valid combinations of prime numbers, marked by OOOOOO}
    \label{fig:prime_tabel}
\end{figure}
